### 2025-01-17 inst/reproduce_results_CP/myrvollnilsen2022.Rmd
Now supports systematic biases
Systematic biases can now be described using an RW2 process. Also added other stuff, including code to reproduce the results of the most recent paper

<!-- Paper_results.md is generated from paper_results.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/results-",
  dev = "png",
  out.width = "80%"
)
```

@@

 plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
      xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy
nsims=3000
results = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) ,
                print.progress=TRUE
                )

@@

```{r biased, eval=TRUE}
results_biased = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE),
                control.bias=list(bias.model="uniform",nsims=nsims,
                                  biasparams = matrix(c(0.98,1.02,0.96,1.04),nrow=2)
                                  ),
                print.progress=TRUE
                )
{
  plot(depth[1+1:n],results_biased$biases$bias1$quant0.975-gicc05,type="l",col="blue",lty=2, xlab="depth", ylab="Simulated time scale - GICC05 (years)",xlim = rev(range(depth)), ylim = c(-2700,2700))
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.975-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], results$simulation$summary$upper-gicc05,col="blue",lty=1)
  abline(h=0,lty=3,col="gray")
  lines(depth[1+1:n], results$simulation$summary$lower-gicc05,col="blue",lty=1)
  lines(depth[1+1:n], results_biased$biases$bias1$quant0.025-gicc05,col="blue",lty=2)
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.025-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], NGRIP_5cm$MCE[1+1:n],col="black",lwd=2)
  legend(1660,2700,legend=c("MCE","Unbiased","2% bias rate", "4% bias rate"),
       col=c("black","blue","blue","blue"),lty=c(1,1,2,3),lwd=c(2,1,1,1),cex=0.65)
}
```

@@

  control.linramp_dust = list(proxy=logdust,interval=interval_dust,interval.unit="index",
                         depth.ref=depth.reference, #imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         rescale.y.factor=-20,
                         imp.fit=TRUE,
                         silent=2L,
                         label=paste0(eventnumber," (logCa):", event_intervals[eventnumber,2])
                         )

@@

```{r events_table, eval=TRUE}
colnames = c("d18O_mean","d18O_q0.025","d18O_q0.975",
             "Ca_mean","Ca_q0.025","Ca_q0.975")
depthresults = t(depthstats)[,2:7]
colnames(depthresults)=colnames
rownames(depthresults)=rownames
ageresults = t(agestats[2:7,])
colnames(ageresults)=colnames
rownames(ageresults)=rownames
```

>>>>

<!-- myrvollnilsen2022.md is generated from myrvollnilsen2022.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/reproduce/myrvollnilsen2022/results-",
  dev = "png",
  out.width = "100%"
)
```

@@

 plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
      xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy
nsims=3000
results = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) 
                )

@@

```{r biased, eval=TRUE}
results_biased = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE),
                control.bias=list(bias.model="uniform",nsims=nsims,
                                  biasparams = matrix(c(0.98,1.02,0.96,1.04),nrow=2)
                                  )
                )
{
  plot(depth[1+1:n],results_biased$biases$bias1$quant0.975-gicc05,type="l",col="blue",lty=2, xlab="depth", ylab="Simulated time scale - GICC05 (years)",xlim = rev(range(depth)), ylim = c(-2700,2700))
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.975-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], results$simulation$summary$upper-gicc05,col="blue",lty=1)
  abline(h=0,lty=3,col="gray")
  lines(depth[1+1:n], results$simulation$summary$lower-gicc05,col="blue",lty=1)
  lines(depth[1+1:n], results_biased$biases$bias1$quant0.025-gicc05,col="blue",lty=2)
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.025-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], NGRIP_5cm$MCE[1+1:n],col="black",lwd=2)
  legend(1660,2700,legend=c("MCE","Unbiased","2% bias rate", "4% bias rate"),
       col=c("black","blue","blue","blue"),lty=c(1,1,2,3),lwd=c(2,1,1,1),cex=0.65)
}
```

@@

  #rescale logdust proxy to avoid having to retune priors again
  rescale.y.factor = -20
  control.linramp_dust = list(proxy=logdust,interval=interval_dust,interval.unit="index",
                         depth.ref=depth.reference, #imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         rescale.y.factor=rescale.y.factor,
                         imp.fit=TRUE,
                         silent=2L,
                         label=paste0(eventnumber," (logCa):", event_intervals[eventnumber,2])
                         )

@@

```{r events_table, eval=TRUE}
colnames = c("d18O_mean","d18O_q0.025","d18O_q0.975",
             "Ca_mean","Ca_q0.025","Ca_q0.975")
depthresults = t(depthstats)[,2:7]
colnames(depthresults)=colnames
rownames(depthresults)=rownames
ageresults = t(agestats[2:7,])
colnames(ageresults)=colnames
rownames(ageresults)=rownames

cat("Onset depth estimates:\n",sep="")
print(depthresults)
cat("Onset age estimates:\n",sep="")
print(ageresults)
```
